PROTEST

### 2019-09-12 article/main.tex
article: sprig --> sprout
change scripts names

    Here, saplings were taken into account. Viable deciduous saplings and coppice sprigs were considered as unidentified deciduous. Their basal area could therefore be assigned to oak and/or beech afterwards. Viable coniferous saplings were considered as unidentified coniferous. Their basal area could therefore be assigned to fir and/or spruce afterwards. Since we had no information on the identity of the non-viable saplings, we assigned their basal area to deciduous and coniferous saplings depending on the relative proportion of these two categories. Plots whose composition was not among the 7 expected compositions were dropped at this stage.

@@

  where $Dg_i$ and $Dg_j$ are the quadratic diameters of species $i$ and $j$; $\alpha$ and $\beta_{1-X}$, parameters to estmiate; and $\varepsilon$, the model residuals. We applied the same variable selection procedure as the one we applied to the site index model (see the three mixture-specific final models in SI). Here, we used $Dg_i$ and $Dg_j$ obtained from "true mixtures", i.e. PROTEST plots where the two mixed species represented more than 75\% of the total basal area of trees (saplings were not taken into account since we do not know their identity).

>>>>

    Here, saplings were taken into account. Viable deciduous saplings and sprouts were considered as unidentified deciduous. Their basal area could therefore be assigned to oak and/or beech afterwards. Viable coniferous saplings were considered as unidentified coniferous. Their basal area could therefore be assigned to fir and/or spruce afterwards. Since we had no information on the identity of the non-viable saplings, we assigned their basal area to deciduous and coniferous saplings depending on the relative proportion of these two categories. Plots whose composition was not among the 7 expected compositions were dropped at this stage.

@@

  where $Dg_i$ and $Dg_j$ are the quadratic diameters of species $i$ and $j$; $\alpha$ and $\beta_{1-X}$, parameters to estimate; and $\varepsilon$, the model residuals. We applied the same variable selection procedure as the one we applied to the site index model (see the three mixture-specific final models in SI). Here, we used $Dg_i$ and $Dg_j$ obtained from "true mixtures", i.e. PROTEST plots where the two mixed species represented more than 75\% of the total basal area of trees (saplings were not taken into account since we do not know their identity).
